### 2021-07-04 docs/manuscript/manuscript.tex
Rephrase Abstract::Methods

\subsection*{Methods}
In this study we used a genetic algorithm in order to explore the genotypic
space of three-node GRNs capable of producing a band expression pattern in a
group of cells. In contrast to previous studies, we explore multiple input
network designs that enable more morphogen interpretation mechanisms to arise.

>>>>

\subsection*{Methods}
In this study we apply a Markov chain Monte Carlo (MCMC)-like algorithm to probe
the design space of three-node GRNs with the ability to generate a band-like
expression pattern (target phenotype) in the middle of an arrangement of 30
cells, which resemble a simple (1-D) morphogenetic field in a developing embryo.
Unlike the majority of modeling studies published so far, here we explore the
space of GRN topologies with nodes having the potential to perceive differently
the same input signal. This allows for a lot more flexibility during the search
space process, and thus enables us to identify a larger set of potentially
interesting and realizable morphogen interpretation mechanisms.
